Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-10 demystify.tex

\begin{table}
    \caption{MS vs. PhD}\label{tab:phd-vs-ms}
    \centering
    \small
    \begin{tabular}{c|c|c}
    \toprule
    \textbf{} & \textbf{MS} & \textbf{PhD} \\
    \midrule
    Objective & Industry & Research \\
    Admission Req & Research experience & No research experience \\
    Coursework Req & Yes & Yes (research is much more important)  \\
    Duration & 2 years & 5--7 years \\
    Adviser Req & No & Yes \\
    Funding & No & Yes \\
    \bottomrule
    \end{tabular}
  \end{table}

>>>>

\begin{table}
    \caption{MS vs. PhD}\label{tab:phd-vs-ms}
    \centering
    \small
    \begin{tabular}{c|c|c}
    \toprule
    \textbf{} & \textbf{MS} & \textbf{PhD} \\
    \midrule
    Objective & Industry & Research \\
    Admission Req & No research experience & Research experience \\
    Coursework Req & Yes & Yes (research is much more important)  \\
    Duration & 2 years & 5--7 years \\
    Adviser Req & No & Yes \\
    Funding & No & Yes \\
    \bottomrule
    \end{tabular}
  \end{table}
